---
title: "Appendix"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align='center')
knitr::opts_chunk$set(comment = NA, message = FALSE, warning = FALSE, cache=FALSE)

library(car)
library(MASS)
library(plyr)
library(ggplot2)
library(lsmeans)
library(multcomp)

options(contrasts = c("contr.sum", "contr.poly"))
```

### Table 1: Structure of Data

```{r}
# Read in data and set structure

adapt <- read.table("C:\\Users\\Dylan\\Documents\\school\\STAT 545\\adapt.txt",sep="",col.names=c("Potato","Regime","Temp","Photo","Leakage"))
adapt$Photo <- NULL
adapt$Potato <- factor(ifelse(adapt$Potato==1,"Species1","Species2"))
adapt$Regime <- factor(ifelse(adapt$Regime==1,"Cold","RoomTemp"))
adapt$Temp <- factor(ifelse(adapt$Temp==1,"-4 Degrees","-8 Degrees"))
attach(adapt)
str(adapt)
```

### Table 2: Summary of Cell Means

```{r}
# Fitting the full interaction model

myfit <- lm(Leakage ~ Potato*Regime*Temp)
yhat <- myfit$fitted.values
resid <- myfit$residuals

# Summarizing cell means

Leakage.sum <- ddply(adapt, .(Potato,Regime,Temp), function(.df){
  data.frame(n = length(.df$Leakage),
             mean = mean(.df$Leakage),
             var = var(.df$Leakage),
             sd = sd(.df$Leakage)
             )
})
Leakage.sum
```

### Plot 1: Comparing Variances Across Groups

```{r,fig.height=4}
# Plot marginal boxplots

p <- ggplot(adapt, aes(x = Potato, y = Leakage, fill = Regime))
p <- p + geom_hline(aes(yintercept = mean(Leakage.sum[,5])), colour = "black", linetype = "dashed", size = 0.3, alpha = 0.5)
p <- p + geom_boxplot(size = 0.15, alpha = 0.4)
#p <- p + geom_point(position = position_dodge(.75), alpha = 0.5)
p <- p + facet_grid(. ~ Temp)
p <- p + scale_fill_manual(values=c("dodgerblue", "sienna1"))
p <- p + stat_summary(fun.y = "mean", geom = "text", label = "----",color= "red", show.legend=FALSE, position = position_dodge(.75))
p <- p + ggtitle(bquote(atop(.("Ion leakage by species, regime, and temperature "), atop(.("Grand mean depicted by grey dashed line, cell means by red dashed line"),""))))
print(p)
```

\newpage

### Table 3: Fitting Full 3-Way Interaction Model

```{r}
# Fitting the full interaction model

myfit <- lm(Leakage ~ Potato*Regime*Temp)
yhat <- myfit$fitted.values
resid <- myfit$residuals

# ANOVA of full interaction model

myanovat3 <- Anova(myfit,type=3)
myanovat3
```

### Plot 2: Diagnostics of Full Model

```{r,fig.height=3}
# Plotting diagnostics
par(mfrow=c(1,2))
par(mar=c(5.1,4.1,2,2.1))
plot(myfit, which = c(1,2))
par(mar=c(5.1,4.1,4.1,2.1))
par(mfrow=c(1,1))
```

### Table 4: Tests for Normality, Constant Variance and Outliers

```{r}
# Testing for equal variance and normality
leveneTest(Leakage~Potato*Regime*Temp,center=median)
shapiro.test(resid)
outlierTest(myfit)
```

### Plot 3: Boxcox Transformation

```{r,fig.height=4,fig.width=4}
# Transforming response variable

#min(Leakage)
Leakage.t <- Leakage + abs(min(Leakage)) + .01 # Adding min to make all values positive
#min(Leakage.t)
myfit.t <- lm(Leakage.t ~ Potato*Regime*Temp) # Creating new fit (not yet transformed)
bc <- boxcox(myfit.t)
title("Boxcox Transformation Plot",cex.main=.85)
ci <- c(min(bc$x[bc$y > max(bc$y) - 1/2 * qchisq(.95,1)]),max(bc$x[bc$y > max(bc$y) - 1/2 * qchisq(.95,1)]))
#ci
#bc$x[which.max(bc$y)]
lambda <- 1/3

Leakage.t <- Leakage.t^(lambda) # Transforming response variable
myfit.t <- lm(Leakage.t ~ Potato*Regime*Temp) # New fit using transformed response
yhat.t <- myfit.t$fitted.values
resid.t <- myfit.t$residuals
```

### Table 5: Fitting Full 3-Way Interaction Model

```{r}
myanovat3.t <- Anova(myfit.t,type=3)
myanovat3.t
```


### Plot 4: Diagnostics of Transformed Response Model

```{r,fig.height=3.5}
# Plotting diagnostics

par(mfrow=c(1,2))
plot(myfit.t, which = c(1,2))
par(mfrow=c(1,1))
```

### Table 6: Tests for Normality, Constant Variance and Outliers in Transformed Model

```{r}
# Testing for equal variance and normality

leveneTest(myfit.t,center=median)
shapiro.test(resid.t)
outlierTest(myfit.t)
```

### Plot 5: Boxcox Transformation (post transformation)

```{r,fig.height=4,fig.width=4}
# Varifying no further transformation recommended
boxcox(myfit.t)
title("Boxcox Transformation Plot (Post Transformation)",cex.main=.85)
```

### Table 7: Summary of Transformed Cell Means

```{r}
# Summarizing cell means

adapt$Leakage.t <- Leakage.t
Leakage.t.sum <- ddply(adapt, .(Potato,Regime,Temp), function(.df){
  data.frame(n = length(.df$Leakage.t),
             mean = mean(.df$Leakage.t),
             var = var(.df$Leakage.t),
             sd = sd(.df$Leakage.t)
             )
})
Leakage.t.sum
```

\newpage

### Plot 6: Profile Plots (before reduction of model)

```{r,fig.height=9.8,fig.width=7.5}
# Plotting profile plots

par(mfrow=c(3,2))

with(adapt[which(Potato=="Species1"),], interaction.plot(x.factor = Temp, trace.factor = Regime, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Potato: Species 1", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Potato=="Species2"),], interaction.plot(x.factor = Temp, trace.factor = Regime, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Potato: Species 2", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Regime=="Cold"),], interaction.plot(x.factor = Potato, trace.factor = Temp, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Regime: Cold", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Regime=="RoomTemp"),], interaction.plot(x.factor = Potato, trace.factor = Temp, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Regime: Room Temp", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Temp=="-4 Degrees"),], interaction.plot(x.factor = Regime, trace.factor = Potato, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Temperature: -4 Degrees", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Temp=="-8 Degrees"),], interaction.plot(x.factor = Regime, trace.factor = Potato, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Temperature: -8 Degrees", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

par(mfrow=c(1,1))
```

```{r,fig.height=2.8}
### Same plots using lsmeans (before reduction of model)

#lsmip(myfit.t, Regime ~ Temp|Potato, ylab = "Ion Leakage (Transformed)")
#lsmip(myfit.t, Temp ~ Potato|Regime, ylab = "Ion Leakage (Transformed)")
#lsmip(myfit.t, Potato ~ Regime|Temp, ylab = "Ion Leakage (Transformed)")
```

### Table 8: Reduced ANOVA Type 3 Model

```{r}
# Reducing model

myfit.t.r <- update(myfit.t, . ~ . - Potato:Regime:Temp)
yhat.t.r <- myfit.t.r$fitted.values
resid.t.r <- myfit.t.r$residuals
myanovat3.t.r <- Anova(myfit.t.r,type=3)
myanovat3.t.r

#myfit.t.r <- lm(Leakage.t ~ Potato + Regime + Temp + Potato*Regime + Regime*Temp)
#myanovat3.t.r <- Anova(myfit.t.r,type="III")
#myanovat3.t.r

#myfit.t.r <- lm(Leakage.t ~ Potato + Regime + Temp + Potato*Regime)
#myanovat3.t.r <- Anova(myfit.t.r,type="III")
#myanovat3.t.r
```

### Plot7: Plotting Diagnostics of Reduced Model

```{r,fig.height=3.5}

# Plotting diagnostics
par(mfrow=c(1,2))
plot(myfit.t.r, which = c(1,2))
par(mfrow=c(1,1))
```

### Table 9: Tests for Normality, Constant Variance and Outliers in Reduced Model

```{r}
leveneTest(myfit.t,center=median)
shapiro.test(resid.t)
outlierTest(myfit.t)
```

\newpage

### Plot 8: Profile Plots (after reduction of model)

```{r,fig.height=9.8,fig.width=7.5}
# Plotting profile plots

par(mfrow=c(3,2))

with(adapt[which(Potato=="Species1"),], interaction.plot(x.factor = Temp, trace.factor = Regime, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Potato: Species 1", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Potato=="Species2"),], interaction.plot(x.factor = Temp, trace.factor = Regime, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Potato: Species 2", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Regime=="Cold"),], interaction.plot(x.factor = Potato, trace.factor = Temp, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Regime: Cold", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Regime=="RoomTemp"),], interaction.plot(x.factor = Potato, trace.factor = Temp, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Regime: Room Temp", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Temp=="-4 Degrees"),], interaction.plot(x.factor = Regime, trace.factor = Potato, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Temperature: -4 Degrees", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

with(adapt[which(Temp=="-8 Degrees"),], interaction.plot(x.factor = Regime, trace.factor = Potato, response = Leakage.t, fun = mean, type = "b", legend = TRUE, ylab = "Ion Leakage (Transformed)", main = "Temperature: -8 Degrees", cex.main = 1, pch = c(1,19),ylim=c(min(Leakage.t.sum[,5]),max(Leakage.t.sum[,5]))))

par(mfrow=c(1,1))
```

```{r,fig.height=2.8}
### Same plots using lsmeans (after reduction of model)
#lsmip(myfit.t.r, Regime ~ Temp|Potato, ylab = "Ion Leakage (Transformed)")
#lsmip(myfit.t.r, Temp ~ Potato|Regime, ylab = "Ion Leakage (Transformed)")
#lsmip(myfit.t.r, Potato ~ Regime|Temp, ylab = "Ion Leakage (Transformed)")
```

\newpage

### Plot 9: Comparing Variances Across Groups (before and after transformation)

```{r,fig.height=4}
# Plot marginal boxplots

p <- ggplot(adapt, aes(x = Potato, y = Leakage, fill = Regime))
p <- p + geom_hline(aes(yintercept = mean(Leakage.sum[,5])), colour = "black", linetype = "dashed", size = 0.3, alpha = 0.5)
p <- p + geom_boxplot(size = 0.15, alpha = 0.4)
#p <- p + geom_point(position = position_dodge(.75), alpha = 0.5)
p <- p + facet_grid(. ~ Temp)
p <- p + scale_fill_manual(values=c("dodgerblue", "sienna1"))
p <- p + stat_summary(fun.y = "mean", geom = "text", label = "----",color= "red", show.legend=FALSE, position = position_dodge(.75))
p <- p + ggtitle(bquote(atop(.("Ion leakage by species, regime, and temperature"), atop(.("Grand mean depicted by grey dashed line, cell means by red dashed line"),"(before transformation)"))))
print(p)
```

```{r,fig.height=4}
# Plot marginal boxplots

p.t <- ggplot(adapt, aes(x = Potato, y = Leakage.t, fill = Regime))
p.t <- p.t + ylab("Ion Leakage (Transformed)")
p.t <- p.t + geom_hline(aes(yintercept = mean(Leakage.t.sum[,5])), colour = "black", linetype = "dashed", size = 0.3, alpha = 0.5)
p.t <- p.t + geom_boxplot(size = 0.15, alpha = 0.4)
#p.t <- p.t + geom_point(position = position_dodge(.75), alpha = 0.5)
p.t <- p.t + facet_grid(. ~ Temp)
p.t <- p.t + scale_fill_manual(values=c("dodgerblue", "sienna1"))
p.t <- p.t + stat_summary(fun.y = "mean", geom = "text", label = "----",color= "red", show.legend=FALSE, position = position_dodge(0.75))
p.t <- p.t + ggtitle(bquote(atop(.(""), atop(.(""),"(after transformation)"))))
print(p.t)
```

```{r}
#lsmeans(myfit.t.r, list(pairwise ~ Potato            ), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Regime            ), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Temp              ), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Potato|Regime     ), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Potato|Temp       ), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Regime|Temp       ), adjust = "tukey")
#lsmeans(myfit.t, list(pairwise ~ Potato|Temp|Regime), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Potato|Regime|Temp), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Temp|Potato|Regime), adjust = "tukey")
#lsmeans(myfit.t.r, list(pairwise ~ Regime|Temp|Potato), adjust = "tukey")
```

```{r,fig.height=4}
#mytukey.rg <- ref.grid(myfit.t.r)
mytukey.t.r <- lsmeans(myfit.t.r, ~ Potato|Regime|Temp, level=.95, adjust = "tukey", method = "pairwise")
#mytukey
#mytukey2 <- lsmeans(myfit.t, ~ Potato|Regime|Temp, level=.95, adjust = "tukey", method = "pairwise")
#mytukey2
#str(mytukey)
#mytukey.sum <- summary(mytukey, ~ Potato|Regime|Temp, level = .95, adjust = "tukey")
#mytukey.sum
#class(mytukey.sum)

#contrast(tukeylsmeans, method = "pairwise")
#mytukey.lsm <- lsmeans(mytukey.rg, ~ Potato|Regime|Temp)
#plot(mytukey.lsm, comparisons = TRUE, alpha = 0.95)

#xtbl <- xtable(mytukey.lsm, caption = "Example", lable = "xtable:example")
#print(xtbl,table.placement = "t")
#cat("See Table~\\ref{xtable:example}.\n")
```

\newpage

### Plot 10: Pairwise Comparison of Means

```{r,fig.height=2.8,fig.width=5}
plot(mytukey.t.r, by = "Potato", level = .95, ylab = "",xlab = "Ion Leakage (Transformed)",cex=.6)
plot(mytukey.t.r, by = "Regime", level = .95, ylab = "",xlab = "Ion Leakage (Transformed)",cex=.6)
plot(mytukey.t.r, by = "Temp", level = .95, ylab = "",xlab = "Ion Leakage (Transformed)",cex=.6)
```

### Table 10: Summaries of Significant Contrasts

```{r}
#library(multcomp)
#lsmeans(myfit.t.r, list(pairwise ~ Potato|Regime|Temp), adjust = "tukey")
mydata <- adapt
mydata$Potato <- as.factor(ifelse(mydata$Potato=="Species1","S1","S2"))
mydata$Regime <- as.factor(ifelse(mydata$Regime=="Cold","C","RT"))
mydata$Temp <- as.factor(ifelse(mydata$Temp=="-4 Degrees","4","8"))
myfit.t.r2 <- lm(Leakage.t ~ Potato*Regime*Temp,data=mydata)
myfit.t.r2 <- update(myfit.t.r2, . ~ . - Potato:Regime:Temp)
glht.p <- glht(myfit.t.r2, linfct = lsm(pairwise~Temp|Potato|Regime), group="Tukey")
glht.r <- glht(myfit.t.r2, linfct = lsm(pairwise~Potato|Regime|Temp), group="Tukey")
glht.t <- glht(myfit.t.r2, linfct = lsm(pairwise~Regime|Temp|Potato), group="Tukey")
lsm.p <- lsmeans(myfit.t.r2, list( pairwise ~ Temp| Potato | Regime | Temp ), adjust = "tukey" )
lsm.r <- lsmeans(myfit.t.r2, list( pairwise ~ Potato | Regime | Temp ), adjust = "tukey" )
lsm.t <- lsmeans(myfit.t.r2, list( pairwise ~ Regime | Temp | Potato), adjust = "tukey" )
lsm.p$`pairwise differences of contrast, Potato | Potato`
lsm.r$`pairwise differences of contrast, Regime | Regime`
lsm.t$`pairwise differences of contrast, Temp | Temp`
#plot( lsm1$`pairwise differences of contrast, Regime | Regime` )
#summary(glht.p)
#summary(glht.r)
#summary(glht.t)
```

\newpage

### Plot 11: Pairwise Differences of Ion Leakage

```{r,fig.height=8,fig.width=7}
par(mfrow=c(3,2))
par(mar=c(5.1,8,4.1,2.1))

plot(glht.p$`Potato = S1`,xlab="Pairwise Differences in Mean Ion Leakage",main="Potato: Species 1 ",cex=.8,cex.main=.8)
plot(glht.p$`Potato = S2`,xlab="Pairwise Differences in Mean Ion Leakage",main="Potato: Species 2 ",cex=.8,cex.main=.8)

plot(glht.r$`Regime = C`,xlab="Pairwise Differences in Mean Ion Leakage",main="Regime: Cold ",cex=.8,cex.main=.8)
plot(glht.r$`Regime = RT`,xlab="Pairwise Differences in Mean Ion Leakage",main="Regime: Room Temp ",cex=.8,cex.main=.8)

plot(glht.t$`Temp = 4`,xlab="Pairwise Differences in Mean Ion Leakage",main="Temp: -4 Degrees ",cex=.8,cex.main=.8)
plot(glht.t$`Temp = 8`,xlab="Pairwise Differences in Mean Ion Leakage",main="Temp: -8 Degrees ",cex=.8,cex.main=.8)

par(mar=c(5.1,4.1,4.1,2.1))
par(mfrow=c(1,1))
```

\newpage

### Pairwise differences across Potato Species Cells

The mean ion leakage of potato species 2 acclimatized to cold weather and later subjected to -4 degree temperatures was significantly \textbf{lower} than those acclimatized to room temperature and later subjected to -8 degree temperatures.

- Estimated difference: $`r round((-1.7192)^3,3)`$ ($p < 0.001$)

The mean ion leakage of potato species 2 subjected to -4 degree temperatures and acclimatized to cold weather was significantly \textbf{lower} than those acclimatized to room temperature.

- Estimated difference: $`r round((-1.3738)^3,3)`$ ($p < 0.001$)

The mean ion leakage of potato species 2 subjected to -8 degree temperatures and acclimatized to cold weather was significantly \textbf{lower} than those acclimatized to room temperature.

- Estimated difference: $`r round((-0.3454)^3,3)`$ ($p < 0.001$)

- This suggests that the mean ion leakage of potatos species 2 acclimatized to cold weather was significantly \textbf{lower} than those acclimatized to room temperature, regardless of the temperature they were later subjected to. (I.e., \textbf{main effect of regime on ion leakage within Potato=Species 2 cell}.)

---

### Pairwise differences across Regime Cells

The mean ion leakage of potato species 1 acclimatized to cold weather and subjected to -4 degree temperatures was significantly \textbf{lower} than potato species 2 which were also acclimatized to cold weather but later subjected to -8 degree temperatures.

- Estimated difference: $`r round((-.8451)^3,3)`$ ($p = 0.002$)

The mean ion leakage of potato species 1 acclimatized to cold weather and subjected to -8 degree temperatures was significantly \textbf{higher} than potato species 2 which were also acclimatized to cold weather but subjected to -4 degree temperatures.

- Estimated difference: $`r round((-.7335)^3,3)`$ ($p = 0.008$)

The mean ion leakage of potato species 1 acclimatized to room temperature and subjected to -4 degree temperatures was significantly \textbf{lower} than potato species 2 which were also acclimatized to room temperature but later subjected to -8 degree temperatures.

- Estimated difference: $`r round((-1.5213)^3,3)`$ ($p < 0.001$)

The mean ion leakage of potato species 1 acclimatized to room temperature and subjected to -8 degree temperatures was significantly \textbf{lower} than potato species 2 which were also acclimatized to room temperature but later subjected to -4 degree temperatures.

- Estimated difference: $`r round((-.8974)^3,3)`$ ($p = 0.003$)

The mean ion leakage of potatos acclimatized to room temperature and subjected to -4 degree temperatures was significantly \textbf{lower} in potato species 1 than potato species 2.

- Estimated difference: $`r round((-1.176)^3,3)`$ ($p < .001$)

The mean ion leakage of potatos acclimatized to room temperature and subjected to -8 degree temperatures was significantly \textbf{lower} in potato species 1 than potato species 2.

- Estimated difference: $`r round((-1.2427)^3,3)`$ ($p < .001$)

- This suggests that the mean ion leakage of potatos acclimatized to room temperature was significantly \textbf{lower} among potato species 1 than potato species 2, regardless of the temperature they were later subjected to. (I.e., \textbf{main effect of species on ion leakage within Regime=Room Temp cell}.)

The mean ion leakage of potato species 1 acclimatized to cold weather and later subjected to -4 degree temperatures was significantly \textbf{lower} than those subjected to -8 degree temperatures.

- Estimated difference: $`r round((-0.7559)^3,3)`$ ($p < 0.001$)

The mean ion leakage of potato species 2 acclimatized to cold weather and later subjected to -4 degree temperatures was significantly \textbf{lower} than those subjected to -8 degree temperatures.

- Estimated difference: $`r round((-0.8227)^3,3)`$ ($p = 0.002$)

- This suggests that the mean ion leakage of potatos acclimatized to cold weather and subjected to -4 degree temperatures was significantly \textbf{lower} than those subjected to -8 degree temperatures, regardless of species. (I.e., \textbf{main effect of temperature on ion leakage within Regime=Cold cell}.)

---

### Pairwise differences across Temperature Treatment Cells

- The mean ion leakage of potato species 1 subjected to -4 degree temperatures and acclimatized to cold weather was significantly \textbf{lower} than potato species 2 which were also subjected to -4 degree temperatures but acclimatized to room temperature.

- Estimated difference: $`r round((-1.39626)^3,3)`$ ($p < .001$)

The mean ion leakage of potato species 1 subjected to -8 degree temperatures and acclimatized to cold weather was significantly \textbf{lower} than potato species 2 which were also subjected to -8 degree temperatures but acclimatized to room temperature.

- Estimated difference: $`r round((-.98578)^3,3)`$ ($p < .001$)

- This suggests that the mean ion leakage of potato species 1 acclimatized to cold weather was significantly \textbf{lower} than potato species 2 which were acclimatized to room temperature, regardless of the temperature they were later subjected to. (I.e., \textbf{two-way interaction effect of species and regime on ion leakage}.)